\section{Experience}

\cventry{09/2019 - 12/2023 (expected)}
{Ph.D. researcher}
{Tilburg University} % Company
{} % Where
{Department of Methodology and Statistics}   % Extra Info
{
    \vspace{0.1em}
    \begin{spacing}{1.1}
    \begin{itemize}
        \item \textbf{Software development} | I developed software for addressing missing data in social science surveys in collaboration with the sociology department at Tilburg University. I contributed to a variety of existing R packages in the field of social science. I developed numerous web applications to facilitate interaction with my research results.
        \item \textbf{Academic research} | I have created innovative algorithms to tackle non-response bias in social surveys and written scientific articles detailing their effectiveness and uses.
        \item \textbf{Development of educational material} | I designed tutorials and study material for university students to practice and evaluate their computational and statistical skills. I developed a website to share accessible blog posts on statistical concepts (see the `Digital garden` on my personal website).
        \item \textbf{Frontal teaching} | I taught university master students how to program and perform complex data analyses in R. I recorded instructional videos to facilitate hybrid learning.
    \end{itemize}
    \end{spacing}
    \vspace{1em}
}

\cventry{08/2018 - 06/2019}
{Teaching assistant}
{Tilburg University} % Company
{} % Where
{Department of Methodology and Statistics}   % Extra Info
{
    \vspace{0.1em}
    \begin{spacing}{1.1}
    I held \textbf{frontal lectures} and \textbf{computer laboratory sessions} for courses on:
    \begin{itemize}
        \item \textit{Computational statistics} (master's level.)
		\item \textit{Statistics and methodology} (master's level.)
		\item \textit{Experimental research methods} (bachelor's level.)
    \end{itemize}
    \end{spacing}
    \vspace{1em}
}

\cventry{03/2017 - 05/2017}
{Research assistant}
{IRVAPP} % Company
{Trento, Italy} % Where
{}   % Extra Info
{
    \vspace{0.1em}
    \begin{itemize}
        \item Data cleaning for a public policy evaluation project.
    \end{itemize}
}

